\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-05-22 paper/ms.tex
improve kepler-10b plot

NASA's \kepler and \ktwo missions have provided some of the most precise, long term monitoring of stars to date \cite{citationneeded}. \kepler has delivered time-series photometry >200,000 objects in the visible with a four year long baseline, allowing for continuous monitoring of potential exoplanet hosting systems and characterization of host stars.

Since the loss of a second reaction wheel in 2009 the Kepler mission was repurposed into the K2 mission.

In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.

>>>>

NASA's \kepler and \ktwo missions have provided some of the most precise,
long term monitoring of stars to date \cite{citationneeded}. \kepler~ has delivered
time-series photometry of more than 200,000 objects in the visible spectrum with a four
year long baseline, allowing for continuous monitoring of potential exoplanet hosting
systems and characterization of host stars.

Since the loss of a second reaction wheel in 2009, the \kepler~ mission was repurposed
into the \ktwo~ mission.

In the near future the \tess mission will deliver high-precision time series data for
90\% of the sky, providing light curves for X millions of objects \cite{citationneeded}.
